\chapter{Buggy Showcase Chair}
\label{ch:Showcase Chair}
This chapter covers all aspects of Buggy Showcase not specified in the Rules.
Especially tips on how to make everything flow smoothly.

\section{Terms}
For clarity, the Design Competition specified in the rules is held during the
Buggy Showcase. The Buggy Showcase is an overarching event which can include
music, slideshows, keynote speakers, bouncy castles, laser tag, or any number
of fun things.

\section{Design Competition}
\label{sec:Design Comp}
The Design Competition should be your top priority. If Buggy Showcase consists
of nothing but the Design Competition, you will have fulfilled the duties of
your role.

\subsection{Space}
You will need to reserve a space that is large enough to accomodate every buggy
the teams will be racing this year, plus any extras they may wish to bring.
Typically Wiegand Gym is used and provides plenty of space given the current
number of teams.
\\\\
You will need to order stanchions to separate the teams from each other
and from the observers. The Sweepstakes Advisor can help you with the ordering
process.
\\\\
You will need to reserve a space separate from the display space large enough
for all the judges, three presenters and one buggy. Connan in the CUC is
large enough, and conveniently located close to the Gym. Be sure to reserve
it early since it may be popular during Carnival. You will also need to order
at least two tables and multiple chairs for this room. The judges need to sit
and the presenters need a place to put their buggy that is not on the floor.

\subsection{Judges}
You will need to find knowledgeable people capable of listening to
presentations and making informed decisions on the quality of the design
and construction of the team's buggies. Start this process early, as it is
often the most challenging part of your job.
\\\\
Professors are usually a good choice. Specifically professors in engineering
or science who have a background close to that used in buggy development.
Volunteers from an organization sponsoring Sweepstakes are also good
candidates. Alumni are typically avoided, especially alumni who are well-known
in the Buggy community or who are very recently graduated. If they are so
old and unknown that no one even knows that they did Buggy, then that should be
fine.

\subsection{Judging Sheets}
The judging sheets have undergone many iterations in past years. You should
look on the Sweepstakes Google Drive for past versions and absolutely
consult previous Showcase Chairs about what did and did not work regarding
the sheets. The judges probably gave feedback about the sheets last year
and you don't want to be the person who didn't implement the changes for
this year.

\subsection{Timing}
Do your best to come up with a schedule that ends early, and try to stick
to it. You will probably run late, as judges will often take a long time to
deliberate or take a very long lunch. Onee thing that can help with this
is to have all teams entering the Design Competition arrive 1-2 hours before
the teams who are not competing. This way all teams are still present for the
display portion, but they don't have to sit around for hours while the
judging takes place.
\\\\
A very important point to remember during Design Comp is that the rest of
the Sweepstakes Committee is essentially sitting on their hands for the
entire time, so don't be afraid to utilize them so you can run around less.

\subsection{Food}
You will need to order breakfast for the judges and Sweepstakes, and lunch
for the teams, the judges, and Sweepstakes. Typically lunch consists of a few
King Kong pizzas. Just be sure that the judges are able to get food before
the mob of hungry students descends upon it.


\section{Buggy Showcase}
\label{sec:Showcase}
Buggy Showcase is designed to make the event more interesting and engaging
for the public and the teams. If you choose, it can start a few hours later
than the Design Competition but end at the same time to ensure maximum
capacity at any given time and minimize the feeling of emptiness that
results from people filtering in and out over the course of four hours.

\subsection{Presenters}
An obvious thing to do during Buggy Showcase is to have one or more presenters
speak about the history of Buggy or their personal experiences with Buggy. In
order for this to be successful, you will need to order a stage and arrange
for a soundsystem. ABTech can probably help with the soundsystem unless they're
busy that day, and you might be able to reuse the stage that Sweepstakes
purchases for the timing system on Raceday.
\\\\
Typically alumni give presentations, but the current students could also
present. You could have each team present an overview of their team.
You could even judge these overviews and present awards if you wanted to.
You could also just put up a Powerpoint that cycles through old pictures.

\subsection{Kid Zone}
Alumni Relations likes to host a Kid Zone for kids who come to Buggy Showcase.
You should work with them to give them space in the room, and order tables
or other supplies if they need them. Hopefully they will mostly take
care of themselves.

\subsection{BAA}
The Buggy Alumni Association needs a table at Buggy Showcase since a large
number of alumni come back for this event. But they should also be mostly
self-contained in their setup and operations.

\subsection{Buggy Books}
You will need to provide a place to sell the Buggy Books as Buggy Showcase is
the time when most books are sold. Someone needs to man the table at all times,
but you can delegate that responsibility to the Buggy Book Chair.


\section{Awards}
The winners of Design Comp are not announced at the event, but are saved
until the Awards Ceremony on Sunday of Carnival. These are some of the
most exciting to announce, since the race winners are known prior to the
ceremony. If the Chairman is amenable to it and you want to announce
the winners, you should! The hard work is over and this is your reward.
